%&pdflate
\documentclass[10pt]{article}
 \textwidth 15cm
 \oddsidemargin 0.0in 
 \evensidemargin 0.0in 
 \topmargin 0in
 \headheight -0in
 \headsep 0in
 \topskip 0in
 \textheight 23.0cm
 \marginparwidth 0in

\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

%%%%%%%%%%%%% REMOVE TO GET PAGE NUMBERS BACK %%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\thispagestyle{empty}

\begin{document}

\linespread{1.0}



{\center
{\Large\bf Joyal John \\ Software Engineer \vspace{0.1in} }

\begin{center} 
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
	Tel:   +44 7514377414\\
	Email: JoyalJohn3500@gmail.com \\
\end{tabular*}
\end{center}


\addtolength{\itemsep}{-1ex} \addtolength{\topsep}{-1.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section*{\bf  Professional Skills}
\begin{center}
\begin{tabular}{c c c c}
{\bf Languages (fluent)}: & Python & Java & Bash\\
{\bf Languages (basic)}: &  PHP & JavaScript & SQL\\
{\bf Cloud \& Deployment}: Docker & Github\\
{\bf IDEs} & Python IDE & VsCode & Android Studio \\
{\bf OS}: & Windows & Linux \\
{\bf Version control}: & Git \\

\end{tabular}
\end{center}


\section*{\bf Summary}

As a software engineer studying Computer Science at the University of Northampton, I have developed strong technical skills and a solid understanding of programming concepts and principles. Some of my key skills and achievements include:

Strong proficiency in multiple programming languages, including Java, Python, and Bash.
Experience with software development methodologies such as Agile and Waterfall models, as well as familiarity with software engineering tools such as Git.
Knowledge of databases and data structures, including SQL and SQLite databases.
Experience with front-end technologies such as HTML, CSS, and JavaScript.
Strong problem-solving and analytical skills, with a track record of developing creative solutions to complex technical challenges.

Excellent communication and teamwork skills, with experience collaborating with cross-functional teams to develop and deliver high-quality software.
During my studies, I have completed relevant coursework, projects, and internships that have honed my skills and provided me with valuable hands-on experience. I am also passionate about technology and committed to continuous learning and professional development, as demonstrated by my participation in extracurricular activities and hobbies related to software engineering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section*{\bf Projects}
{\bf Blackboard Assignment}, (Java, Android Studio) [February 2023 - March 2023]
\setlength{\itemsep}{0.10ex}
\item Created a blackboard using Java in Android Studio as well as xml layouts to create a login system, with individual logins and multiple activities; fully functional notes application, calculator app, dice roller game, and a quiz with save files.

\item {\bf Shell Scripting Assignment}, (Bash, Linux OS, Area of Rectangle Program and Blackjack Program) [December 2022 - January 2023]
\setlength{\itemsep}{0.10ex}
\item Area of a Rectangle program involved in inputting two measurements with a choice of either centimetres or inches, and calculating the correct answer of the area in whatever measurement you choose fit. Blackjack game involved scripting inputs to allow users to hit or stay, and be up against the computer with a live betting system.



\section*{\bf Work Experience}


{\bf App Development with Jacob P Wilson}, (Data Scientist at PPX Consulting) [July 2022 - September 2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item My work for Jacob involved in the creation of an admin portal login system for a time tracker, with use of HTML, CSS and JavaScript. 
\item Gained many valuable lessons in independent work such as talking to clients to ascertain
business requirements, as well as working under a deadline.
\end{itemize}

{\bf Other Work Experience} [pre-2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item General work around multiple warehouses of DPD and The Co-operative as a picker packer whilst maintaining the warehouse; given me a lot of transferable and valuable communication skills, with a strong work ethic in addition.
\end{itemize}



\section*{\bf Education}
\begin{center}  % put inside center environment
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}llr}
{\bf B.Sc.}	& 	Computer Science	\bf{University of Northampton}& 	2021-2024 	\\
		
\end{tabular*}
\end{center} 




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PERSONAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section*{\bf Personal skills}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  Art Skills - Tonals
\item  Photography Skills - Landscape and Cityscapes Photographs
\item  Amateur Weightlifter
\item  Badminton
\end{itemize}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%	 EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\section*{\bf References}
Jacob P Wilson {\bf Data Scientist at PPXFinancialConsulting} \newline
Tel: +44 7510 385 493 \textbar Email: jacob@ppxconslting.co.uk \newline




\end{document}